NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-05-31 ms_nihao_budget.tex
fix the problem on figure 3
rephrased some English

%% FIGURE 3
\begin{figure}
\centerline{
  \psfig{figure=ratioprofile_v4.eps,width=0.5\textwidth}
}
\caption{Baryon distribution of each galaxy from NIHAO simulations. 
 The lines are color coded by their halo mass, which shows a
  clear trend that the more massive haloes preserve more baryons at
  all radii.}
\label{fig:rps}
\end{figure}

@@

The observations and the simulations match well in every phase {\bf
  except} the cool CGM gas, where the observations find $3\times$ the
mass that simulations predict.  If the observations are correct, the
simulations have either ejected {\bf cool gas too far}, or  they have
created a CGM with the wrong mix of gas temperatures. The total gas
fractions (0.39 in COS-HALOs, 0.41 in NIHAO) suggest the latter
option.   {\bf However, \citet{Stern16} developed a new method to
  constrain the physical conditions in the cool CGM from measurements
  of ionic  columns densities. This new method combines the
  information available from different ??? during the photoionization
  modeling, and was applied to the COS-HALOs data,  yielding a total
  cool CGM mass within the virial radius of $1.3\times10^{10}\Msun$
  which is shown by the green hashed bar in Fig~\ref{fig:budget} and
  is in good agreement with our prediction.  As the
  Fig.~\ref{fig:corona} and Fig.~\ref{fig:inout} show, the cool gas is
  the most important component in CGM so that the more accurate
  knowledge of the physical properties of CGM are necessary to better
  understand the role of the CGM in galaxy formation.}
%
As the CGM of lower mass galaxies will soon be observed,
Table~\ref{tab:comparison} lists information about CGM
mass fractions of the different components of gas in haloes down to a
halo mass of $\sim 10^{10}\Msun$.

@@

\item {\bf ??? I don't understand this sentence ?? Cool gas is a major
  component in total baryons  whose mass is same as the fiducial
  baryonic mass of  total dark matter mass inside virial radius. Most
  of the cool gas in these baryons locates out of the virial radius.}

>>>>

%% FIGURE 3
\begin{figure}
\centerline{
  \psfig{figure=ratioprofile.eps,width=0.5\textwidth}
}
\caption{Baryon distribution of each galaxy from NIHAO simulations. 
 The lines are color coded by their halo mass, which shows a
  clear trend that the more massive haloes preserve more baryons at
  all radii.}
\label{fig:rps}
\end{figure}

@@

The observations and the simulations match well in every phase {\bf
  except} the cool CGM gas, where the observations find $3\times$ the
mass that simulations predict.  If the observations are correct, the
simulations have either ejected {\bf cool gas too far}, or  they have
created a CGM with the wrong mix of gas temperatures. The total gas
fractions (0.39 in COS-HALOs, 0.41 in NIHAO) suggest the latter
option.   {\bf However, \citet{Stern16} developed a new method to
  constrain the physical conditions in the cool CGM from measurements
  of ionic  columns densities. This new method combines the
  information available from different sightlines during the photoionization
  modeling, and was applied to the COS-HALOs data,  yielding a total
  cool CGM mass within the virial radius of $1.3\times10^{10}\Msun$
  which is shown by the green hashed bar in Fig~\ref{fig:budget} and
  is in good agreement with our prediction.  As the
  Fig.~\ref{fig:corona} and Fig.~\ref{fig:inout} show, the cool gas is
  the most important component in CGM so that the more accurate
  knowledge of the physical properties of CGM are necessary to better
  understand the role of the CGM in galaxy formation.}
%
As the CGM of lower mass galaxies will soon be observed,
Table~\ref{tab:comparison} lists information about CGM
mass fractions of the different components of gas in haloes down to a
halo mass of $\sim 10^{10}\Msun$.

@@

\item {\bf Cool gas is a major component of the total baryons within
      R$_{\rm bar}$, most of which is outside of the virial radius.}
